---
title: "Example"
author: "Surina"
date: "2023-04-26"
output: html_document
editor_options: 
  chunk_output_type: console
---
The first step is to install required packages
```{r}
# dplyr and tidyver packages are for pre-processing / cleaning data
# skimr is for skim the dataset
# DataExplorer is for explore data and doing descriptive analysis
# psych is the most commonly used package for psychology
# ShinyItemAnalysis is also for doing item analysis
# ggplot2 is for drawing plots

install.packages(c("dplyr", "tidyverse","skimr", "DataExplorer", 
                   "psych", "ShinyItemAnalysis", "ggplot2"))
```

The second step is to load these packages
```{r}
library("dplyr")
library("tidyverse")
library("skimr")
library("DataExplorer")
library("psych")
library("ShinyItemAnalysis")
library("ggplot2")
```

We can import our data now! 
```{r}
# read excel data, using readxl package
install.packages("readxl") 
library("readxl")
Example<-read_excel("Example.xlsx")

# read csv data, using 
install.packages("readr") 
library("readr")
Example<-read.csv("Example.csv")
write_sav(Example, "Example.sav")

# read sav (i.e., spss) data
install.packages("haven") 
library("haven")
Example<-read_sav("Example.sav")
```

Check the descriptive statistics of the dataset using skim function in skimr package

It reports number of missing data in each variable (n_missing), complete rate, mean,
standard deviation (sd), the minimum value (P0), number in the first quartile (P20),
median (P50), number in the third quartile (P7), the maximum value (P100), and 
histogram for the data frequency distribution (hist)
```{r}
skimr::skim(Example)
```

Check the descriptive statistics of the dataset using describe function in psych package

It reports nnumber of cases in each variable (n), mean, standard deviation (sd), 
median, complete rate, mean,trimmed mean, median absolute deviation (mad), 
the minimum value (min), the maximum value (P100), range, skewness, kurtosis,  
and standard error (se)

In general, a skewness value between -1 and 1 indicates a relatively symmetrical distribution, 
while values outside of this range indicate a skewed distribution. 
For kurtosis, a value of 0 indicates a normal distribution, negative values indicate a flatter distribution, and positive values indicate a more peaked distribution. But kurtosis values 
between -2 and 2 are often considered acceptable for most statistical analyses.
```{r}
psych::describe(Example)
```










